It's Never Too Late To Learn\\ \emph{Using Online Machine Learning in Distributed Systems}

### 2016-01-22 writeups/msr_workshop/paper.tex
more content

@@

What features of the run-time system are important to the ML agent? How can they
be captured effectively? Can the ML agent learn from incomplete data? For
example, if an ML agent needs to make decisions regarding performance
optimization, would ignoring garbage collection activities or the VMM result in
corrupting the learned model? How sensitive should the learner be?

- quesiton of what features to include is there, but being conservative usually the right
way to go
- bigger quesiton is how ml component deals with omissions and other problems. Separate
into failure sections? Yeah, replace this with ``failures'' and move feature selection stuff
down to last section
How could routine
distributed systems issues such failures and delays in an asynchronous setting affect the
learning system?

\subsection*{Hierarchy}
Distributed systems are often designed in a hierarchical manner, where
subcomponents are monitoring and managing others. These components and layers of
indirection simplify reasoning about the system at large. However, it is not
clear how hierarchy will affect an ML agent.
\begin{itemize}
  \item Will hierarchy aid the learning system via parallelism? Or will it hinder
    it since not all features are visible at every level?
  \item Should learning happen in each component of the system? Or should it be
    centralized?
  \item If learning is happening at multiple levels of the hierarchy, will that
    create interference between the learners? Or will they complement each
    other?
\end{itemize}

- Should feature vectors cut across the levels or not?
- In general should be composable if at each level can define decision and reward,
and exploration randomization is different at each level

@@

An ML agent can be trained offline with pre-labeled data. However, is this
possible in the context of distributed systems? An online learning systems is
more logical in this context, however, how do we quantify the costs of
exploration vs exploitation of learned strategies?

- Probably omit this, or replace with ``Randomization''. Basically, we already know
that exploratoin-exploitation is the right approach, and that will be encapsulated
by the ML component (its decisions will reflect this, and it will take care of
computing probabilities etc.). But there's an interesting point about inherent randomization
in systems

\section{Expanding the scope}

@@

Opacity (also, which features matter?)
- We are also pursuing work on cracking models open to see what they are doing inside.
There are different ways to gain insight as to what a model is doing. For example a simple
linear model may learn a vector of weights on the supplied features. These weights can be
studied, and indeed some techniques such as lasso are oftne used to reduce the number of features. However, these
techniques need to be handled carefully. Just becasue a feature has 0 weight doesn't mean it
can be removed: perhaps it is unimportant preceisely because it exists, and its removal all of
asudden changes the weight on other features.

>>>>

While reward information is also not available at the decision location, this is
the norm in contextual learning settings, where reward information is only
discernible after a delay and often by a separate subsystem. Thus, we do not
expect this to pose a problem. (The faster reward information is collected, the
faster the resulting datapoint can be used by the learning subsystem.)

@@

The disparity in locality above results in a lack of fate sharing between the
distributed system components involved in a decision.  Failures in any of
htese components have implications on the inputs to the learning system. For
example, server failures in a load balanced cluster could mean that certain
context information is staler than others or unavailable altogether. How do we
convey this ''lack of information'' to the learning system, and how does it
cope with sporadically incomplete data? Should failures be encoded in the
context somehow?

Failures in distributed systems are hard to distinguish from asynchrony in some
cases. What other ways does asynchrony affect the learning system?

There is another failure mode in which important contextual information is
simply not captured due to designer ommision. In general contextual learning
algorithms scale very well with the size of the size of the context, so it is
generally a good idea to include more data than necessary. In some cases,
however, it may not be easy to access this data, e.g. obtaining statistics
about a background garbage collection process or about a VMM.

\subsection*{Hierarchy}

Distributed systems are often designed in a hierarchical manner, where
subcomponents monitor and manage others. These components and layers of
indirection simplify reasoning, building, and maintaining the system at
large. However, it is not clear how hierarchy should be handled with respect to
optimizing decisions via contextual learning. In general contextual learning is
composable, in that decisions of subcomponents can be used to influence
higher-level components, downstream components can make decisions influenced by
the decisions of upstream components, and so on.  Should the context for each
decision be limited to the level it is at in the hierarchy, or is it better for
contexts to span multiple (or all) levels? Should decision points roughly mimic
the hierarchy of the system? Consider deep memory hierarchy, for example. One
could imagine that by capturing contextual information across the entire
hierarchy, one could decide at what level to cache a piece of data, instead of
only deciding on the current level and relying on evictions to move between
levels.

\ignore{
\begin{itemize}
  \item Will hierarchy aid the learning system via parallelism? Or will it hinder
    it since not all features are visible at every level?
  \item Should learning happen in each component of the system? Or should it be
    centralized?
  \item If learning is happening at multiple levels of the hierarchy, will that
    create interference between the learners? Or will they complement each
    other?
\end{itemize}
}

@@

Contextual learning uses exploration (controlled randomization) to discover
potentially good strategies. This is the famous explore-exploit tradeoff and is
well established to be necessary for proper online optimization. Randomization
can be encapsulated and handled by the learning system, but there are two
situations in which it might emerge to the systems level. First, if multiple
components are making decisions independently, it is important to ensure that
thre randomization used by each (e.g. the seed passed to the learning system)
are independent of each other. Second, many distributed systems already use
randomization inherently, such as randomized load balancing or randomized cache
eviction strategies. Can this randomization be leveraged by the learning
system to achieve its exploration goals naturally?

\ignore{
An ML agent can be trained offline with pre-labeled data. However, is this
possible in the context of distributed systems? An online learning systems is
more logical in this context, however, how do we quantify the costs of
exploration vs exploitation of learned strategies?
}

\ignore{
\section{Expanding the scope}

@@

Opacity (also, which features matter?)
- We are also pursuing work on cracking models open to see what they are doing inside.
There are different ways to gain insight as to what a model is doing. For example a simple
linear model may learn a vector of weights on the supplied features. These weights can be
studied, and indeed some techniques such as lasso are oftne used to reduce the number of features. However, these
techniques need to be handled carefully. Just becasue a feature has 0 weight doesn't mean it
can be removed: perhaps it is unimportant preceisely because it exists, and its removal all of
asudden changes the weight on other features.
}
